### 2024-08-16 manuscript.tex
Results description

>>>>

The observations show cloud occurrence peaking at the surface, whereas models
show higher peak (at about 500 m). The models underestimate total cloud
fraction by 10--20\%, and show a strong decrease in cloud occurrence near the
surface, but this is not happening in the observations. ICON and ERA5
overestimate cloud occurrence at the peak (between 0--1 km). Above 1 km, ICON
and MERRA-2 understimate cloud occurrence, but ERA5 is very accurate. The too
high peak in models is partly supported by the LCL distribution, which peaks
higher in the models then in the observations (at the surface), although this
is not very pronounced. The northern zone shows stronger peak of cloud
occurrence near the surface than the southern zone, and this could be because
higher latitudes have more unstable atmospheric profiles. The northern and
southern zones show similar biases in models as in the general case, but ERA5
does not overestimate the peak in the northern zone (near-surface cloud
occurrence is still strongly understimated). Cyclonic situations have a larger
amount observed cloudiness, including the peak and total cloud fraction. In
these situations, the models are doing a relatively good job of getting the
vertical profile of cloud occurrence right, but still tend to underestimate
cloud occurrence above 1 km and near the surface. Non-cyclonic situations are
similar to the general case. In stable stituations cloud occurrence peaks
strongly at the surface in observations, compared to unstable situations, where
the peak is more more obtuse and spread across 0--1 km. In stable situations
the models are doing a fairly good job, but overestimate cloud occurrence at
the peak below 1 km, above 1 km the show similar biases as in the general case.
In unstable situations the bias in ICON is very pronounced, with a much
stronger peak at about 500 m, ERA5 is underestimating cloud occurrence below 1
km (especially near the surface), and MERRA-2 even more strongly. In all
situations, even when the models overestimate cloud occurrence at some
altitudes, they always substantially underestimate the total cloud fraction.
ICON can be generally characterised as substantially overestimating cloud
occurrence below 1 km and underestimating above, underestimating the total
cloud fraction, and showing greatest biases in unstable and non-cyclonic
conditition. It also shows peak of cloud occurrence at higher altitude than obs
(500 m vs. near the surface) and correspondingly its LCL tends to be also
higher. MERRA-2 can be generally characterised as underestimating cloud
occurrence at nearly all altitudes as well as the total cloud fraction, but
mostly above and below 500 m (the peak at 500 m is well-represented). It
struggles the most in the northern zone, and in unstable situations. ERA5 can
be generally characterised as representing cloud occurrence correctly above
about 1--1.5 km, overestimating below, but underestimating near-surface cloud
occurrence (0--500 m). The total cloud fraction is strongly understimated in
all situations. It has tendency towards understimation in the northern zone and
unstable stiuations, and conversely overestimating in the southern zone and
stable conditions.
